\begin{center}

\textbf{Acknowledgments}
\end{center}
\addcontentsline{toc}{chapter}{Acknowledgments}
\bigskip

It was the end of a decade, but the start of an age. The completion of this doctoral dissertation marks a significant milestone in my academic journey, a feat that would not have been possible without the guidance, support, and encouragement of many individuals. I am deeply grateful for the opportunity to express my sincere appreciation to those who have made the completion of this thesis possible. 

First and foremost, I would like to express my deepest gratitude to my Ph.D. supervisor, Prof. Yuan Wu, for his invaluable guidance and unwavering support throughout my Ph.D. study. His deep academic insight, rigorous research standards, and professional dedication have fundamentally shaped my understanding of research. I am deeply indebted to him for the time and patience he has invested in my development --- not only as a researcher but also as a scholar pursuing excellence --- and for exemplifying that scholarship is both discipline and devotion.

I extend my heartfelt thanks to my colleagues in the laboratory, whose companionship and collaboration have made the long path of research far less solitary. Their camaraderie and constructive discussions foster a vibrant academic atmosphere. This laboratory has been the fertile soil in which my academic identity has taken root.

To my family, they are the silent bedrock upon which this achievement stands. Words often fail to capture the depth of their sacrifice and the constancy of their love. In moments when the weight of this journey threatened to crush my resolve, their unconditional belief became the anchor that held me steady. They have been a safe harbor throughout this voyage, and this glory belongs as much to them as to me.

I also acknowledge the University of Macau for providing the facilities and resources necessary for the successful completion of this thesis. It has offered a stimulating and conducive environment for academic research and personal growth, and it has been an honor to be part of this esteemed community.

Ultimately, degrees are temporary, but the gratitude I hold is immutable. I dedicate this work to all who have illuminated my path, and whose support has been my constant companion. This dissertation is a testament that while the journey was mine to walk, I never walked it alone.


