\begin{thebibliography}{999}
\addcontentsline{toc}{chapter}{References}
%\markboth{References}{References}

\bibitem{ABG06} \textsc{P.-A. Absil, C. G. Baker, and K. A. Gallivan},
{\em A truncated-CG style method for symmetric generalized eigenvalue problems},
J. Comput. Appl. Math., 189 (2006), pp. 274--285.

\bibitem{ABG07}\textsc{P.-A. Absil, C. G. Baker, and K. A. Gallivan},
{\em Trust-region methods on Riemannian manifolds},
Found. Comput. Math., 7 (2007), pp. 303--330.

\bibitem{AG06}\textsc{P.-A. Absil and K. A. Gallivan},
{\em Joint diagonalization on the oblique manifold for independent component analysis},
In Proceedings of the IEEE International Conference on Acoustics, Speech, and Signal Processing (ICASSP),
Vol. 5, pp. V-945--V-948, 2006.

\bibitem{AMS08}\textsc{P.-A. Absil, R. Mahony, and R. Sepulchre},
{\em Optimization Algorithms on Matrix Manifolds},
Princeton University Press, Princeton, 2008.

\bibitem{AM12}\textsc{P.-A. Absil and J. Malick},
{\em Projection-like retractions on matrix manifolds}, SIAM J. Optim., 22 (2012), pp. 135--158.

\bibitem{AMSP02}\textsc{P.-A. Absil, R. Mahony, R. Sepulchre, and P. Van Dooren},
{\em A Grassmann-Rayleigh quotient iteration for computing invariant subspaces},
SIAM Rev., 44 (2002), pp. 57--73.

\bibitem{ASPM06}\textsc{P.-A. Absil, R. Sepulchre, P. Van Dooren, and R. Mahony},
{\em Cubically convergent iterations for invariant subspace computation},
SIAM J. Matrix Anal. Appl., 26 (2006), pp. 70--96.

\bibitem{ADM02}\textsc{R. L. Adler, J.-P. Dedieu, J. Y. Margulies, M. Martens, and M. Shub},
{\em Newton's method on Riemannian manifolds and a geometric model for the human spine},
IMA J. Numer. Anal., 22 (2002), pp. 359--390.

\bibitem{APJ92}\textsc{T. A. Arias, M. C. Payne, and J. D. Joannopoulos},
{\em Ab initio molecular dynamics: Analytically continued energy functionals
and insights into iterative solutions}, Phys. Rev. Lett., 69 (1992), pp. 1077--1080.



\bibitem{BAG06}\textsc{C. G. Baker, P.-A. Absil, and K. A. Gallivan},
{\em An implicit Riemannian trust-region method for the symmetric generalized
eigenproblem}, In Vassil N. Alexandrov, Geert Dick van Albada, Peter M.A. Sloot, and Jack Dongarra, editors,
Computational Science--ICCS 2006, Vol. 3991 of LNCS, pp. 210--217, Springer, New York, 2006.

\bibitem{Bai12}\textsc{Z. J. Bai, S. Serra-Capizzano, and Z. Zhao},
{\em Nonnegative inverse eigenvalue problems with partial eigendata},
 Numer. Math., 120 (2012), pp. 387--431.

\bibitem{BDDRV00}\textsc{Z. Bai, J. Demmel, J. Dongarra, A. Ruhe, and H. van der Vorst},
{\em  Templates for the Solution of Algebraic Eigenvalue Problems}, SIAM, Philadelphia, 2000.

\bibitem{BHMST08}\textsc{T. Betcke, N. J. Higham, V. Mehrmann, C. Schr\"{o}der, and F. Tisseur},
{\em  NLEVP: A collection of nonlinear eigenvalue problems},
Technical report MIMS EPrint 2008.40, School of Mathematics, The University of Manchester, 2008.
http://www.manchester.ac.uk/mims/eprints.

\bibitem{BZ82}\textsc{P. Bendt and A. Zunger},
{\em New approach for solving the density-functional self-consistent-field problem},
Phys. Rev. B, 26 (1982), pp. 3114--3137.

\bibitem{Bernstein}\textsc{D. Bernstein},
{\em Matrix Mathematics -- Theory, Facts, and Formulas},
2nd edition, Princeton University Press, Princeton, 2009.

\bibitem{B03}\textsc{D. P. Bertsekas},
{\em Nonlinear Programming}, 2nd edition, Athena Scientific, Belmont, 1999.

\bibitem{B07}\textsc{W. M. Boothby},
{\em An Introduction to Differentiable Manifolds and Riemannian Geometry},
Revised 2nd edition, Academic Press, London, 2007.

\bibitem{B05}\textsc{C. Le Bris},
{\em Computational chemistry from the perspective of numerical analysis},
Acta Numer., 14 (2005), pp. 363--444.

\bibitem{BHN99}\textsc{R. H. Bryd, M. E. Hbribar, and J. Nocedal},
{\em An interior point algorithm for large-scale nonlinear programming},
SIAM J. Optim., 9 (1999), pp. 877--900.



\bibitem{CB00}\textsc{E. Canc\`{e}s and  C. L. Bris},
{\em On the convergence of SCF algorithms for the Hartree-Fock equations},
Math. Model. Numer. Anal., 34 (2000), pp. 749--774.

\bibitem{R. Chan and X. Jin}\textsc{R. Chan and X. Jin},
{\em An Introduction to Iterative Toeplitz Solvers},
SIAM, Philadelpha, 2007.

\bibitem{CHERNCL98}\textsc{S. S. Chern, W. H. Chen, and K. S. Lam},
{\em Lectures on Differential Geometry}.
World Scientific, River Edge, NJ, 1998.

\bibitem{CL11}\textsc{X. Chen and D. L. Liu},
{\em Isospectral flow method for nonnegative inverse eigenvalue problem with prescribed structure},
J. Comput. Appl. Math., 235 (2011), pp. 3990--4002.

\bibitem {C98}\textsc{M. T. Chu},
{\em Inverse eigenvalue problems}, SIAM Rev., 40 (1998), pp. 1--39.

\bibitem{CDS04}\textsc{M. T. Chu, F. Diele, and I. Sgura},
{\em Gradient flow method for matrix completion with prescribed eigenvalues},
Linear Algebra Appl., 379 (2004), pp. 85--112.

\bibitem{CD91}\textsc{M. T. Chu and K. R. Driessel},
{\em Constructing symmetric nonnegative matrices with prescribed eigenvalues by differential equations},
SIAM J. Math. Anal., 22 (1991), pp. 1372--1387.

\bibitem {CG02}\textsc{M. T. Chu and G. H. Golub},
{\em Structured inverse eigenvalue problems}, Acta Numer., 11 (2002), pp. 1--71.

\bibitem{CG05}\textsc{M. T. Chu and G. H. Golub},
{\em Inverse Eigenvalue Problems: Theory, Algorithms, and Applications}, Oxford University Press, Oxford, 2005.

\bibitem{CG98}\textsc{M. T. Chu and Q. Guo},
{\em A numerical method for the inverse stochastic spectrum problem}, SIAM J. Matrix Anal. Appl., 19 (1998), pp. 1027--1039.

\bibitem{CKZ98} \textsc{J. E. Cohen, J. H. B. Kemperman, and G. Zb\u{a}ganu},
{\em Comparisons of Stochastic Matrices with Applications in Information Theory, Statistics,
Economics and Population Sciences}, Birkh\"{a}user, Boston, 1998.

\bibitem{CEH12}\textsc{S. J. Cox, M. Embree, and J. M. Hokanson},
{\em One can hear the composition of a string: Experiments with an inverse eigenvalue problem},
SIAM Rev., 54 (2012), pp. 157--178.



\bibitem{D03}\textsc{B. N. Datta},
{\em Numerical Methods for Linear Control Systems : Design and Analysis},
Elsevier Academic Press, New York, 2003.

\bibitem{DFK96}\textsc{T. De Luca, F. Facchinei, and C. Kanzow},
{\em  A semismooth equation approach to the solution of nonlinear complementarity problems},
Math. Program., 75 (1996), pp. 407--439.

\bibitem{DC76}\textsc{M. P. do Carmo},
{\em Differeital Geometry of Curves and Surfaces},
Prentice-Hall Inc., Englewood Cliffs, NJ, 1976. Translated from the Portuguese.

\bibitem{DC92}\textsc{M. P. do Carmo},
{\em Riemannian Geometry},
Mathematics: Theory \& Applications. Birkh\"{a}user Boston Inc., Boston, MA, 1992.
Translated from the second Portuguese edition by Francis Flaherty.



\bibitem{EAS98}\textsc{A. Edelman, T. A. Arias and S. T. Smith},
{\em  The geometry of algorithms with orthogonality constraints},
SIAM J. Matrix Anal. Appl., 20 (1998), pp. 303--353.

\bibitem{ELN04}\textsc{P. D. Egleston, T. D. Lenker, and S. K. Narayan},
{\em The nonnegative inverse eigenvalue problem}, Linear Algebra Appl., 379 (2004), pp. 475--490.



\bibitem{FEQ10}\textsc{K. Feng and M.Z. Qin},
{\em Symplectic Geometric Algorithms for Hamiltonian System},
Sci. and Tech. Press of Zhejiang: Hangzhou (in Chinese), 2002.

\bibitem{FMMA04}\textsc{J. B. Francisco, J. M. Mart\'{i}nez, and L. Mart\'{i}nez},
{\em Globally convergent trust-region methods for self-consistent field
electronic structure calculations}, J. Chem. Phys., 121 (2004), pp. 10863--10878.

\bibitem{FMM06}\textsc{J. B. Francisco, J. M. Mart\'{i}nez, and L. Mart\'{i}nez},
{\em Density-based globally convergent trust-region methods for
self-consistent field electronic structure calculations},
J. Math. Chem., 40 (2006), pp. 349--377.

\bibitem{FM95}\textsc{M. I. Friswell and J. E. Mottershead},
{\em Finite Element Model Updating in Structural Dynamics},
Kluwer Academic Publishers, Dordrecht, 1995.



\bibitem{GYM09}\textsc{W. Gao, C. Yang, and J. Meza},
{\em Solving a class of nonlinear eigenvalue problems by Newton's method},
Technical report, Lawrence Berkeley National Laboratory, Berkeley, CA, 2009.

\bibitem{G04}\textsc{G. M. L. Gladwell},
{\em Inverse Problems in Vibration},  Kluwer Academic Publishers, 2004.

\bibitem{GV96}\textsc{G. H. Golub and C. F. Van Loan},
{\em Matrix Computations}, 4th edition, Johns Hopkins University
Press, Baltimore, 2013.



\bibitem{HA01}\textsc{W. W. Hager},
{\em Minimizing a quadratic over a sphere},
SIAM J. Optim., 12 (2001), pp. 188--208.

\bibitem{HLW06}\textsc{E. Hairer, C. Lubich, and G. Wanner},
{\em Geometrical Numerical Integration: Structure-Preserving Algorithms for Ordinary Differential Equations},
2nd ed., Springer, Berlin, 2006.

\bibitem{HM94}\textsc{U. Helmke and J. B. Moore},
{\em Optimization and Dynamical Systems}, Springer-Verlag, London, 1994.

\bibitem{H76}\textsc{M. W. Hirsch},
{\em Differential Topology}, GTM 33, Springer-Verlag, New York,  1976.

\bibitem{RHCJ94}\textsc{R. Horn and C. Johnson},
{\em Topics on Matrix Analysis}, Cambridge University Press, Cambridge, 1994.



\bibitem{IMNZ00}\textsc{A. Iserles, H. Z. Munthe-Kaas, S. P. N{\o}rsett, and A. Zanna},
{\em Lie-group methods}, Acta Numer., 9 (2000), pp. 215--365.



\bibitem{JHB07}\textsc{H. B. Ji},
{\em Optimization approcaches on smooth manifolds},
Ph.D. thesis, Department of Information Engineering, Australian National University, 2007.

\bibitem{Jin1}\textsc{X. Jin},
{\em Preconditioning Techniques for Toeplitz Systems},
Higher Education Press, Beijing, 2010.

\bibitem{Jost10}\textsc{J. Jost},
{\em Riemannian Geometry and Geometric Analysis}, Sixth edition, Springer, Berlin, 2011.

\bibitem{JBAS10}\textsc{M. Journ\'{e}e, F. Bach, P.-A. Absil, and R. Sepulchre},
{\em Low-rank optimization for semidefinite convex problems},
SIAM J. Optim., 20 (2010), pp. 2327--2351.



\bibitem{K51}\textsc{F. I. Karpelevi\u{c}},
{\em On the characteristic roots of matrices with nonnegative elements},
Izv. Akad. Nauk SSSR Ser. Mat. 15 (1951), pp. 361--383 (in Russian).

\bibitem{K81}\textsc{G. P. Kerker},
{\em Efficient iteration scheme for self-consistent pseudopotential calculations},
Phys. Rev. B, 23 (1981), pp. 3082--3084.

\bibitem{KL08}\textsc{O. Koch and C. Lubich},
{\em Dynamical low rank approximation},
SIAM J. Matrix Anal. Appl., 29 (2008), pp. 434--454.

\bibitem{KL10}\textsc{O. Koch and C. Lubich},
{\em Dynamical tensor approximation},
SIAM J. Matrix Anal. Appl., 31 (2010), pp. 2360--2375.

\bibitem{KF96}\textsc{G. Kresse and J. Furthm\"{u}ller},
{\em Efficiency of ab-initio total energy calculations for metals and semiconductors using a
plane-wave basis set}, Comput. Mater. Sci., 6 (1996), pp. 15--50.



\bibitem{Lang99}\textsc{S. Lang},
{\em Fundamentals of Differential Geometry},
GTM 191, Springer-Verlag, New York, 1999.

\bibitem{Lee97}\textsc{J. M. Lee},
{\em Riemannian Manifolds: An Introduction to Curvature}, Springer-Verlag, New York, 1997.

\bibitem{Lee00}\textsc{J. M. Lee},
{\em Introduction to Topological Manifolds}, Springer-Verlag, New York, 2000.

\bibitem{Lee03}\textsc{J. M. Lee},
{\em Introduction to Smooth Manifolds}, Springer-Verlag, New York, 2003.

\bibitem{LM08}\textsc{A. S. Lewis and J. Malick},
{\em Alternating projections on manifolds},
Math. Oper. Res., 33 (2008), pp. 216--234.

\bibitem{LNV93}\textsc{X. P. Li, R. W. Nunes, and D. Vanderbilt},
{\em Density-matrix electronic-structure method with linear system-size scaling},
Phys. Rev. B, 47 (1993), pp. 10891--10894.

\bibitem{L13}\textsc{M. M. Lin},
{\em Fast recursive algorithm for constructing nonnegative matrices with prescribed real eigenvalues},
arXiv:1305.7444, 2013.

\bibitem{LWWY13}\textsc{X. Liu, X. Wang, Z. W. Wen, and Y. X. Yuan},
{\em On the convergence of the self-consistent field iteration in Kohn-Sham density functional theory},
SIAM J. Matrix Anal. Appl., 35 (2014), pp. 546--558.



\bibitem{MMMM06}\textsc{D. S. Mackey, N. Mackey, C. Mehl, and V. Mehrmann},
{\em Structured polynomial eigenvalue problems: Good vibrations from good linearization},
SIAM J. Matrix Anal. Appl., 28 (2006), pp. 1029--1051.

\bibitem{MAH94}\textsc{R. E. Mahony},
{\em Optimization algorithms on homogeneous spaces: With applications in linear systems theory},
Ph.D. thesis, Department of Systems Engineering, Australian National University,
77 Massachusetts Avenue, Cambridge, MA 02139--4307, 1994.

\bibitem{MAH96}\textsc{R. E. Mahony},
{\em The constrained Newton method on a Lie group and the symmetric eigenvalue problem},
Linear Algebra Appl., 248 (1996), pp. 67--89.

\bibitem{MHM96}\textsc{R. E. Mahony, U. Helmke, and J. B. Moore},
{\em Gradient algorithms for principal component analysis},
J. Austral. Math. Soc. Ser. B, 37 (1996), pp. 430--450.

\bibitem{MMA02}\textsc{R. E. Mahony and J. H. Manton},
{\em The geometry of the Newton method on non-compact Lie groups},
J. Global Optim., 23 (2002), 309--327.

\bibitem{M02}\textsc{J. H. Manton},
{\em Optimization algorithms exploiting unitary constraints},
IEEE Trans. Signal Processing, 50 (2002), pp. 635--650.

\bibitem{M04}\textsc{J. H. Manton}.
{\em On the various generalisations of optimisation algrithms to manifolds},
In Sixteenth International Symposium on Mathematical Theory of Networks and Systems,
Katholieke Universiteit Leuven, Belgium, 2004.

\bibitem{MMH03}\textsc{J. H. Manton, R. E. Mahony, and Y. Hua},
{\em The geometry of weighted low rank approximations},
IEEE Trans. Signal Processing,  51 (2003), pp. 500--514.

\bibitem{MA04}\textsc{R. M. Martin},
{\em Electronic Structure: Basic Theory and Practical Methods},
Cambridge University Press, Cambridge, 2004.

\bibitem{M11}\textsc{G. Meyer},
{\em Geometric optimization algorithms for linear regression on fixed-rank matrices},
Ph.D. thesis, Department of electrical engineering and computer science,
University of Li\`{e}ge, 2011, http://orbi.ulg.ac.be/handle/2268/97713.

\bibitem{MS97}\textsc{J. M. Millam and G. E. Scuseria},
{\em Linear scaling conjugate gradient density matrix search as an alternative to diagonalization for
first principles electronic structure calculations}, J. Chem. Phys., 106 (1997), pp. 5569--5577.

\bibitem{MM05}\textsc{S. A. Miller and J. Malick},
{\em Newton methods for nonsmooth convex minimization: Connections
among U-Lagrangian, Riemannian Newton and SQP methods},
Math. Program., 104 (2005), pp. 609--633.

\bibitem{M88}\textsc{H. Minc},
{\em Nonnegative Matrices},  Wiley, New York, 1988.

\bibitem{MMHE94}\textsc{J. B. Moore, R. E. Mahony, and U. Helmke},
{\em Numerical gradient algorithms for eigenvalue and singular value calculations},
SIAM J. Matrix Anal. Appl., 15 (1994), pp. 881--902.

\bibitem{MUNK00}\textsc{J. R. Munkres},
{\em Topology}, 2nd edition, Prentice Hall, Upper Saddle River, NJ, 2000.



\bibitem{NP11}\textsc{A. V. Nazin and B. T. Polyak},
{\em Randomized algorithm to determine the eigenvector of a stochastic matrix with application to the PageRank
problem}, Autom. Remote Control, 72 (2011), pp. 342--352.

\bibitem{NW99}\textsc{J. Nocedal and S. J. Wright},
{\em Numerical Optimization}, Springer-Verlag, New York, 1999.



\bibitem{O06}\textsc{R. Orsi},
{\em Numerical methods for solving inverse eigenvalue problems for nonnegative matrices},
SIAM J. Matrix Anal. Appl., 28 (2006), pp. 190--212.

\bibitem{OW00}\textsc{B. Owren and B. Welfert},
{\em The Newton iteration on Lie groups},
BIT, 40 (2000), pp. 121--145.



\bibitem{PTAAJ92}\textsc{M. C. Payne, M. P. Teter, D. C. Allan, T. A. Arias, and J. D. Joannopoulos},
{\em Iterative minimization techniques for ab initio total-energy calculations: Molecular dynamics and conjugate gradients},
Rev. Mod. Phys., 64 (1992), pp. 1045--1097.

\bibitem{P53}\textsc{H. Perfect},
{\em  Methods of constructing certain stochastic matrices}, Duke Math. J., 20 (1953), pp. 395--404.

\bibitem{P55}\textsc{H. Perfect},
{\em  Methods of constructing certain stochastic matrices. II}, Duke Math. J., 22 (1955), pp. 305--311.

\bibitem{PH10}\textsc{S. Petoukhov  and M. He},
{\em Symmetrical Analysis Techniques for Genetic Systems and Bioinformatics: Advanced Patterns and Applications},
Hershey, USA: IGI Global, 2010.

\bibitem{PDS99}\textsc{B. G. Pfrommer, J. Demmel, and H. Simon},
{\em Unconstrained energy functionals for electronic structure calculations},
J. Comput. Phys., 150 (1999), pp. 287--298.

\bibitem{PLU05}\textsc{M. D. Plumbley},
{\em Geometrical methods for non-negative ICA: Manifolds, Lie groups and toral subalgebras},
Neurocomputing, 67 (2005), pp. 161--197.

\bibitem{PR69}\textsc{E. Polak and G. Ribi\`{e}re},
{\em Note surla convergence des m\'{e}thodes de directions conjugu\'{e}es},
Rev. Fr. Imform. Rech. Oper., 16 (1969), pp. 35--43.

\bibitem{P69}\textsc{B. T. Polyak},
{\em The conjugate gradient method in extreme problems},
USSR Comput. Math. Math. Phys., 9 (1969), pp. 94--112.



\bibitem{QGA09}\textsc{C. H. Qi, K. A. Gallivan, and P.-A. Absil},
{\em Riemannian BFGS algorithm with applications}, Recent Advances in Optimization and its Applications in Engineering,
Springer, 2009, pp. 183--192.



\bibitem{RW12}\textsc{W. Ring and B. Wirth},
{\em Optimization methods on Riemannian manifolds and their application to shape space},
SIAM J. Optim., 22 (2012), pp. 596--627.



\bibitem{SI13}\textsc{H. Sato and T. Iwai},
{\em A new, globally convergent Riemannian conjugate gradient method},  arXiv:1302.0125 [math.OC].

\bibitem{SI13-2}\textsc{H. Sato and T. Iwai},
{\em A Riemannian optimization approach to the matrix singular value decomposition}, SIAM J. Optim., 23 (2013), pp. 188--212.

\bibitem{S06}\textsc{E. Senata},
{\em Non-negative Matrices and Markov Chains}, 2nd rev. ed., Springer-Verlag, New York, 2006.

\bibitem{S86}\textsc{M. Shub},
{\em Some remarks on dynamical systems and numerical analysis}, in: Dynamical Systems and
Partial Differential Equations, Proc. VII ELAM (L. Lara-Carrero and J. Lewowicz, eds.),
pp. 69--92, Equinoccio, U. Sim\'{o}n Bol\'{i}var, Caracas, 1986.

\bibitem{S14}\textsc{S. T. Smith},
{\em Optimization techniques on Riemannian manifolds}, arXiv:1407.5965 [math.OC].

\bibitem{S83}\textsc{G. W. Soules},
{\em Constructing symmetric nonnegative matrices}, Linear and Multilinear Algebra, 13 (1983), pp. 241--251.

\bibitem{SO96}\textsc{A. Szabo and N. S. Ostlund},
{\em Modern Quantum Chemistry: An Introduction to Advanced Electronic Structure Theory}, Dover, New York, 1996.



\bibitem{TOY04}\textsc{L. Thogersen, J. Olsen, D. Yeager, P. Jorgensen, P. Salek, and T. Helgaker},
{\em The trust-region self-consistent field method: Towards a black-box optimization in Hartree-Fock and Kohn-Sham theories},
J. Chem. Phys., 121 (2004), pp. 16--27.

\bibitem{TM01}\textsc{F. Tisseur and K. Meerbergen},
{\em A survey of the quadratic eigenvalue problem}, SIAM Rev., 43 (2001), pp. 234--286.

\bibitem{TRL02}\textsc{N. T. Trendafilov and R. A. Lippert},
{\em The multimode Procrustes problem},
Linear Algebra Appl., 349 (2002), pp. 245--264.



\bibitem{UD94}\textsc{C. Udriste},
{\em Convex Functions and Optimization Methods on Riemannian Manifolds},
Mathematics and Its Applications, Vol. 297, Kluwer Academic, Dordrecht, 1994.



\bibitem{VH03}\textsc{J. VandeVondele and J. Hutter},
{\em An efficient orbital transformation method for electronic structure calculations},
J. Chem. Phys., 118 (2003), pp. 4365--4369.

\bibitem{VH02}\textsc{T. Van Voorhis and M. Head-Gordon},
{\em A geometric approach to direct minimization}, Mol. Phys., 100 (2002), pp. 1713--1721.

\bibitem{VV10}\textsc{B. Vandereycken and S. Vandewalle},
{\em A Riemannian optimization approach for computing low-rank solutions of Lyapunov equations},
SIAM J. Matrix Anal. Appl., 31 (2010) pp. 2553--2579.

\bibitem{VOSS04}\textsc{H. Voss},
{\em An Arnoldi method for nonlinear eigenvalue problems}, BIT, 44 (2004), pp. 387--401.



\bibitem{WG09}\textsc{Z. Z. Wen and D. Goldfarb},
{\em Line search multigrid method for large-scale convex optimization}, SIAM J. Optim., 20 (2009), pp. 1478--1503.

\bibitem{WY13}\textsc{Z. Z. Wen and W. T. Yin},
{\em A feasible method for optimization with orthogonality constraints}, Math. Program., 142 (2013), pp. 397--434.



\bibitem{X98}\textsc{S. F. Xu},
{\em An Introduction to Inverse Algebraic Eigenvalue Problems}, Peking University Press and Vieweg Publishing, 1998.



\bibitem{YF97}\textsc{N. Yamashita and M. Fukushima},
{\em Modified Newton methods for solving semismooth reformulations of monotone complementarity problems},
Math. Program., 76 (1997), pp. 469--491.

\bibitem{YMW06}\textsc{C. Yang, J. C. Meza, and L. W. Wang},
{\em A constrained optimization algorithm for total energy minimization in electronic
structure calculations}, J. Comput. Phys., 217 (2006), pp. 709--721.

\bibitem{YMW07}\textsc{C. Yang, J. C. Meza, and L. W. Wang},
{\em A trust region direct constrained minimization algorithm for the Kohn-Sham equation},
SIAM J. Sci. Comput., 29 (2007), pp. 1854--1875.

\bibitem{YGM09}\textsc{C. Yang, W. Gao, and J. C. Meza},
{\em On the convergence of the self-consistent field iteration for a class of nonlinear eigenvalue problems},
SIAM J. Matrix Anal. Appl., 30 (2009), pp. 1773--1788.

\bibitem{YX11}\textsc{S. J. Yang and C. Q. Xu},
{\em Row stochastic inverse eigenvalue problem}, Journal of Inequalities and Applications, 24 (2011), pp. 137--141.



\bibitem{ZZL06}\textsc{L. Zhang, W. J. Zhou, and D. H. Li},
{\em A descent modified Ploak-Ribi\`{e}re-Ployak conjugate gradient method and its global convergence},
IMA J. Numer. Anal., 26 (2006), pp. 629--640.

\bibitem{ZhaoBaiChen13}\textsc{Z. Zhao, Z. J. Bai, and G. Z. Chen},
{\em On the alternating direction method of multipliers for nonnegative inverse eigenvalue problems with partial eigendata},
J. Comput. Appl. Math., 239 (2013), pp. 114--134.

\bibitem{ZhaoBaiJin1}\textsc{Z. Zhao, Z. J. Bai, and X. Q. Jin},
{\em A Riemannian Newton algorithm for nonlinear eigenvalue problems},
SIAM J. Matrix Anal. Appl., 36 (2015), pp. 752--774.

\bibitem{ZhaoBaiJin2}\textsc{Z. Zhao, X. Q. Jin, and Z. J. Bai},
{\em A geometric nonlinear conjugate gradient method for stochastic inverse eigenvalue problems},
SIAM J. Numer. Anal., submitted.


\end{thebibliography}
